Compositional equivalences based on Open pNets

### 2020-03-18 2016-Weak-FH-Bisim/WeakBisim.tex
Update WeakBisim.tex
typos intro,
pour tester GitHub Desktop

Establishing equivalences between programs or system is crucial both for verifying correctness of programs, by establishing that two implementations are equivalent, and for justifying optimisations and program transformations, by establishing that a modified program is equivalent to the source one. There exist several equivalence relations for programs, and bisimulations are among the most versatile of these equivalences. Among bisimulation relations one distinguishes strong bisimulation, that requires that each action of a program is simulated by a single action of the equivalent program, an weak bisimulations that  is a coarser relations, alowing some of the actions to be
  invisible or internal moves, and thus not simulated by the equivalent program.

@@

  refinement preorders ?

  Algorithms ?

@@

\ERIC{
  =>  Expliquer deux versions algos bisim (check/on-the-fly)\\
=> Do we need comment on Simplification ? I'm not sure I can write
something definitive, and Zechen is currently working on it.\\
=> idees pour implementer Weak efficcement (= sans construire WOA) ?}

>>>>

Establishing equivalences between programs or system is crucial both for verifying correctness of programs, by establishing that two implementations are equivalent, and for justifying optimisations and program transformations, by establishing that a modified program is equivalent to the source one. There exist several equivalence relations for programs, and bisimulations are among the most versatile of these equivalences. Among bisimulation relations one distinguishes strong bisimulation, that requires that each action of a program is simulated by a single action of the equivalent program, an weak bisimulations that  is a coarser relations, allowing some of the actions to be
  invisible or internal moves, and thus not simulated by the equivalent program.

@@

@@

\ERIC{
  =>  Expliquer deux versions algos bisim (check/on-the-fly)\\
=> Do we need comment on Simplification ? I'm not sure I can write
something definitive, and Zechen is currently working on it.\\
=> idees pour implementer Weak efficacement (= sans construire WOA) ?}
